ComBatLS Replication Results

### 2024-08-16 paper_lbcc_results.Rmd
notes on scripts used to create inputs:

---
title: "hbm_paper_results"
output: html_document
date: '2023-11-12'
---

Rmd to show and get feedback on planned for results & figures for the combatLS paper. Currently thinking I'll have centile score results be the focus of the paper and keep z-scores for the supplement.

@@

source("./cubic_scripts/R_scripts/gamlss_helper_funs.R")
#source("./cubic_scripts/R_scripts/ranked_welch_tests.R")

>>>>

---
title: "ComBatLS LBCC Results"
output: html_document
date: '2023-11-12'
---

Rmd to compile, test, and visualize ComBatLS vs ComBat-GAM harmonization in the LBCC.

Relies on outputs derived/functions from:
1. `lifespan_eda.Rmd`
2. `run_LBCC_pipeline.sh`
    - `R_scripts/combat_apply_w_transform.R`
    - `R_scripts/fit_lifespan_mod_notbv.R`
    - `R_scripts/fit_lifespan_mod_site_est.R`
3. `run_LBCC_stats.sh`
    - `R_scripts/fit_lifespan_centiles.R`
    - `R_scripts/get_lifespan_site_eff.R`
    - `R_scripts/get_lifespan_deltas.R`

@@

source("./cubic_scripts/R_scripts/gamlss_helper_funs.R")

### 2024-08-16 paper_prop_results.Rmd
notes on scripts used to create inputs:

---
title: ""
output: html_document
date: '2023-11-12'
---

Rmd to show and get feedback on planned for results & figures for the combatLS paper. Currently thinking I'll have centile score results be the focus of the paper and keep z-scores for the supplement.

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
if(!require('pacman')) {
  install.packages('pacman')
}
pacman::p_load(data.table, ggplot2, tidyverse, ggseg, ggsegExtra, paletteer, ggpubr, gridExtra, lemon, parallel, rstatix, lme4, interactions, ggrepel, ggrain, ggh4x, purrr)
#Sys.setenv("MC_CORES"=10L)
options("mc.cores")

source("./cubic_scripts/R_scripts/stats_tests.R")
```

>>>>

---
title: "ComBatLS Varying-Ratio Results"
output: html_document
date: '2023-11-12'
---

Rmd to compile and visualize tests of ComBatLS against other harmonization methods when varying the M:F ratios of each simulated site.

Relies on outputs derived/functions from:

1. `ukb_curation-eda.Rmd`
2. `run_varying_ratios_pipeline.sh`
   - `R_scripts/permute_sites_varying_ratio.R`
   - `R_scripts/combat_apply.R`
   - `R_scripts/fit_perm_basic_mod.R`
   - `R_scripts/fit_centiles.R`
   - `R_scripts/summarise_cent_subj-wise.R`
3. `run_varying_ratios_stats.sh`
   - `R_scripts/summarise_cent_subj-wise.R`
   - `R_scripts/ratio_results.R`
   - `R_scripts/featurewise_sex_bias_test.R`
   - `R_scripts/remove_extremes_single.R`
4. `pull_stats.sh`

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
if(!require('pacman')) {
  install.packages('pacman')
}
pacman::p_load(data.table, ggplot2, tidyverse, ggseg, ggsegExtra, paletteer, ggpubr, gridExtra, lemon, parallel, rstatix, lme4, interactions, ggrepel, ggrain, ggh4x, purrr)
#Sys.setenv("MC_CORES"=10L)
options("mc.cores")
```

### 2024-08-16 paper_replication_results.Rmd
notes on scripts used to create inputs:

---
title: "hbm_paper_results"
output: html_document
date: '2023-11-12'
---

>>>>

---
title: "ComBatLS Replication Results"
output: html_document
date: '2023-11-12'
---

Rmd to compile and visualize tests of ComBatLS against other harmonization methods when replicating site simulations 100x.

Relies on outputs derived/functions from:

1. `ukb_curation-eda.Rmd`
2. `run_permutation_pipeline.sh`
   - `R_scripts/permute_sites_.R`
   - `R_scripts/combat_apply.R`
   - `R_scripts/fit_perm_basic_mod.R`
   - `R_scripts/fit_centiles.R`
   - `R_scripts/summarise_cent_subj-wise.R`
3. `run_permutation_stats.sh`
   - `R_scripts/summarise_cent_subj-wise.R`
   - `R_scripts/ratio_results.R`
   - `R_scripts/featurewise_sex_bias_test.R`
   - `R_scripts/remove_extremes_single.R`
4. `pull_stats.sh`
